{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@

        Let $X_1, X_2, Y$ be Hilbert spaces. 

@@

        The KKT conditions give the following convex feasibility problem 

@@

        Allow $X_1 = \RR^{n_1}, X_2 = \RR^{n_2}, Y = \RR^m$. 

@@

        \begin{theorem}[bounds on the total iterations]

@@

            The total iteration counts is bounded by: 

@@

        \begin{theorem}[restarted GMAPG convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}

@@

>>>>

        \begin{definition}[a linear feasibility problem]
            Let $A\in \RR^{m\times n}$, $b \in \RR^m$
            Let $\mathcal K$ be a simple cone. 
            The linear feasibility problem is defined as the following optimization problem: 
                \min_{x \in \mathcal K} \Vert Ax - b\Vert^2.
        The KKT of a linear programming problem is an instance of a linear feasibility problem. 

@@

        Let $X_1, X_2, Y$ be Euclidean spaces. 

@@

        The KKT conditions give the following linear feasibility problem 

@@

        Assuming $X_1 = \RR^{n_1}, X_2 = \RR^{n_2}, Y = \RR^m$. 

@@

        \begin{theorem}[bounds on the total iterations]\label{thm:rgmapg-total-itr-bnds}

@@

            The total number of iterations is bounded by: 

@@

        \begin{theorem}[restarted GMAPG convergence and complexity]\;\label{thm:rgmapg-cnvg-complexity}\\

@@

            Then it has from Theorem \ref{thm:rgmapg-total-itr-bnds} that:
